A Computational Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-03-30 paper/paper.tex
pass 2/2

RL is a problem-solving technique in which, through their interactions with an external environment,
an agent learns to reach goals, optimize reward signals, or minimize costs
in an iterative trial-by-error fashion.
At any moment, each taken \textit{action} $a$ triggers a changes in the
\textit{state} of the environment
$s \rightarrow s'$, accompanied by a real-valued \textit{reward}
$r = r(s, a)$ (or regret!, since it can be negative) collected by the
agent.
In this view, the environment is partially controlled by
the action of the agent and the reward should be thought
of as satisfaction -- or punishment -- accompanying the execution of
an action.
Action may be delayed to achieve substantial increases in expected reward
that can increase over time.
The environment is generally taken as stochastic,
that is, unpredictable, changing in random ways. In addition,
it is only \textit{partially observed},
in the sense that only part of the current state is observed by
the agent \citep{starkweather2017dopamine}.
This unpredictability of the environment
is realistic in a model which sets out
to explain DMN function. Indeed, it is known that the more the external world is predictable,
the more mental activity becomes detached from the actual sensory inputs
\citep{antrobus1966studies, pope1978regulation},
the more stimulus-independent thoughts occur, and
the higher the neural activity in the DMN.
Conversely, the more the currently executed task is unknown and unpracticed,
the lower the DMN activity
\citep{filler1973daydreaming, teasdale1995stimulus}.
%
These ``offline'' processes may however contribute to
optimizing control of the organism.
Such a framework of DMN funtion based on reinforcement learning
can naturally embed human behavior
in the tension between exploitative action with immediate gains and
explorative action with longer-term reward schedules
\citep{dayan2008decision}.
The implication of the DMN in a diversity of
particularly advanced cognitive processes
can be parsimoneously explained as prediction error minimization
coupled with probabilistic simulations in form of mental scenes,
thus calibrating action portfolios and
maximizing reward outcome at various time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo (MCMC) sampling
\citep{tenenbaum2011grow}.

@@

Computing an optimal policy then corresponds to finding the parameters $\theta^Q_{k+1}$ which minimize the following mean-squared loss function
\begin{equation}
  \mathcal L(\theta^Q_{k+1})
  % = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}[(Q(s, a|\theta^Q) - Q(s',a'|\theta^Q_{k+1}))^2]
  = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}\left[\frac{1}{2}(Q(s, a|\theta^Q_{k+1}) - y)^2\right],
  \label{eq:oracle}
\end{equation}
where
$ y = r + \gamma \max_{a' \in \mathcal A} Q(s', a'|\theta^Q_k) = r + \gamma Q(s', \pi(s')|\theta^Q_k)$ is the prediction target.
% While $y_t$ is also dependent on $\theta^Q$, this is typically ignored.
For instance, a general linear model with a kernel $\phi$ would be of the
form
$${Q}(s, a|\theta^Q) = \phi(s,a)^T\theta^Q.$$
$\phi(s,a)$ would represent a high-level hand-crafted representation of the state-action $(s,a)$ into an appropriate
feature space. Such are the techniques that have been proposed by \cite{songNIPS2016}.
%  and Parr et al. 2003 (JMLR)].
A recently proposed breakthrough alternative
\citep{mnih2015,silver2016mastering}, is to learn this
representation using a deep neural net, leading to the so-called \textit{Deep Q-learning} family of methods which
are by far the current state-of-the-art in RL. In such a case, $\theta^Q$
would correspond to the strengths of low-level synaptic or high-level functional connections between different
neurons / nodes / regions in the network.

Learning of the the entire model parameters can effictively be achieved via \textit{backprop},
wherein prediction errors (aka \textit{regrets})  are propagated from lower to higher regions to modulate the choice of future actions
% online stochastic gradient descent is used to minimize the variational objective
% \eqref{eq:oracle}.

@@

\begin{mdframed}
\textbf{A note on classical RL algorithms.}
Note that most RL algorithms, including \textit{Temporal Difference (TD)}
learning \citep{sutton1998reinforcement}, REINFORCE \citep{williams1992}, and SARSA can be
cast in this general variational framework. For example TD corresponds to
the above framework using a linear value approximator with feature encoding
$\phi(s,a) = \delta_{(s,a)} =  \text{ point mass at }(s,a)$ on the grid
$\mathcal S \times \mathcal A$, and so
$$\nabla_{\theta^Q_{k+1}}Q(s, a|\theta^Q_{k+1}) = \phi(s, a) = \delta_{(s,a)}.$$
%% Whence, the gradient update due to the sample $(s,a,r,s') \in \mathcal D$ is
%% $$\theta^Q(s,a) \leftarrow \theta^Q(s,a) + (Q(s, a|\theta^Q_{k+1}) - y)$$ ??
\end{mdframed}

\subsubsection{Interlude: The role of the hippocampus}
\paragraph{Does the hippocampus do Monte-Carlo sampling ?}
In RL, Monte-Carlo simulation can be used to update the agent's belief state
\citep{silver2010monte}. Such methods have a sample complexity that is determined only by the underlying difficulty of the POMDP, rather than the size of the state space or observation space,
which can be prohibitively large.
Monte-Carlo simulation provides a simple method for evaluating the value / fitness of a state.
They provide an effective mechanism both for tree search and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
observations and rewards. These simulations would be used to update the value function, without ever looking inside the black box describing the model's dynamics. This would be a simple control algorithm by evaluating all legal actions and selecting the action with highest evaluation.
In these challenging POMDPs, Monte-Carlo simulation provides an effective mechanism both for tree search and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.
Much recent work points to Monte Carlo or stochastic sampling– based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. For sampling-based methods it is still almost non-existent beyond the description of receptive fields.

\paragraph{Hippocampal replay = inverse reinforcement-learning ?}
%\begin{mdframed}
  Given the trace $s_0,a_0,s_1,\ldots,$ of an optimal agent's strategy $\pi^*$ in
  a POMDP (called a \textit{teacher's demonstration}), can we figure out what is the
  (instantaneous) reward function $r: \mathcal S \times \mathcal \mathcal A
  \rightarrow \mathbb R$ that the agent is optimizing over a prescribed class of reward functions
  (e.g., linear rewards $r(s,a) \equiv \theta^T\phi(s,a)$)?
  For example, given traces of motor actions from a an adult to grab a cup on a table,
  can an observing child figure out what ``langragian'' functional is being minimized by the former ?
  How ? Can they reproduce this optimal behavior ?
%\end{mdframed}
Such questions are of course pertinent to our decision-making theory for the DMN.
In the general artificial case, the problem has been extensively studied and partially solved by
\cite{abbeel2004}. They are also been rigourously studied in general optimal control literature under the name
``inverse optimal control'', but in model-based certain (where the physical dynamics are known, etc.)...

@@

\subsection{Putting everything together}
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{rl_process_chart.pdf}
  \caption{The DMN as an RL agent...}
  \label{fig:rl_process_chart}
\end{figure}
The DMN is today known to consistently increase in neural
  activity when humans engage in goal-directed behavior that are detached from
  current sensory environment \citep{kenet2003spontaneously, fiser2004small}
  and it was proposed to be situated at the top of the functional network hierarchies
  \citep{carhart2010default, margulies2016situating}.
  Its involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the implicit computation of
  action and state cascades as a function of what happened in the past.
% A policy represents the repertoire of possible actions
%   on the world given a current state. It encodes the probabilites of
%   choosing actions to be executed in a certain situation.
% Interactions between external and internal sources of
%   information are probably commonplace during perception \citep{gershman2010learning}
The DMN may subserve
  constant exploration of possible future actions and their
  cumulative outcomes. Implicit computation of future choices
  provides an explanation for purposeful mind-wandering.

The HC provides perturbed action-transition-state-reward samples
  as a block of "imagined", "hypothesized", "recalled" experience;
  the small variations in these experience blocks allow searching
  a larger space of parameters and possible experiences.
  In the absence of environmental input and feedback
  (e.g., mind-wandering or sleep) pseudo-experiencing (i.e., emulating) possible
  future scenarios and action outcomes.
  Our approach acknowledges the unavoidable stochasticity of
  computation in neuronal processes \citep{faisal2008noise}.

  In our proposed model-free RL-based view, \textit{inference} in the human brain reduces to
  generalization of
  policy and value adaptations from sampled experiences to
  successful action choices and reward predictions in future states.
  As such,
  plasticity in the DMN arises naturally:
  If an agent behaving optimally in a given environment moves
  to novel, yet unexperienced environments, reward prediction errors will
  massively increase. This will lead to adaptation of the policy until the system converges to a 
  new steady-state of optimal action decisions in the volatile environment.

@@

% \begin{figure}[!tb]
%   \centering
%   \includegraphics[width=.8\linewidth]{vae.pdf}
%   \caption{Variational autoencoders...}
%   \label{fig:vae}
% \end{figure}
The main algorithm for minimizing free-energy $F_G^R(\x)$ is the \textit{wake-sleep algorithm}.
\citep{dayan1995helmholtz}. As noted already in \citep{dayan1995helmholtz},
a crucial drawback of the wake-sleep algorithm is that it requires a concurrent models (generative and recogntiion), which together do not correspond to optimization of (a bound of) the marginal likelihood (because of the incorrect KL used therein, etc.). Thus the brain could not possible be running such a algorithm, not even in principle! To the rescue, we note that the recent theory of
\textit{variational auto-encoders (VAEs)} \citep{kingma2013auto} might provide an efficient alternative to the wake-sleep algorithm, as it overcomes the technical limits of the former, by using a reparametrization trick. For example, unlike the wake-sleep algorithm for minimizing free-energy, VAEs can be efficiently trained via back-propagation of learning errors.

@@

\textbf{XXX Your focus in this subsection ought to be on the SC itself not POMPDs, etc.}
 \begin{itemize}
    \item Processing social information has been proposed to underlie the
    physiological baseline of human brain function
    \citep{schilbach2008minds}. This was later challenged by observing
    analogues of the DMN in monkeys \citep{mantini2011default}
    and rats \citep{lu2012rat}, with
    supposedly less advanced social capacities.
    The MDPs parsimoneously explain the dominance of social content in
    human mental scenes by their extremely high relevance to humans
    reflected by high values for social information in the value matrix
    \citep{baker2009action}.
    \item How can a same neurobiological circuit be equally important
    for baseline house-keeping functions and specific task performance?
    Our computational account can explain why the DMN is implicated
    in both a goal-directed task and an idlying rest cognitive set,
    if environmental relevance is processed, manipulated, and retained
    also as a baseline function of human mental activity.
    In tasks, the policy and value matrices are updated to optimize short-term action,
    whereas, at rest, these parameter updates may
    improve especially mid- and long-term action.
    \item The sentinel account does not provide a formal mechanisms of
    how attention and memory resources are exactly reallocated when
    encountering a salient environmental stimulus. \textbf{XXX remove the next sentence. It's probably false.}
    In contrast,
    the Bellman recursion is weighted at each step by
    $\sum_{a \in A}\pi(a|s)$. This factor weighs which action cascades
    are recursively explored by the agent and which decision trees are neglected.
    This directly implies allocation of attention and computational load.
    \item In sum,
    MDPs imply a ``radar'' function of monitoring the environment for salient information
    in general and explain social thinking as a physiological brain baseline
    as an important special case, without excluding other topics
    contemplated in continuous mental activity.
 \end{itemize}

\section{Conclusion}
What brain function could be important enough
for the existence and survival of the human species
to warrant constant, high energy costs?
MDPs provide an attractive
process model how the human association cortex
might implement supra-modal representation and control of the environment to
optimize the organism's fate.
% by obtaining reward and avoiding pain.
This idealized process model explains
a number of previous experimental observations in the
DMN by a simple but non-trivial mechanism.
%
From the computational viewed of a Markov decision process,
behavior unfolds by integrating happened past events
and possible future events to guide action choice in the present context.
This functional account is more compatible with the DMN's
poorly understood involvement across
autobiographical memory retrieval, problem solving,
abstract reasoning based on internally generated scenes, social cognition,
as well as delay discounting and self-related prospection.
MDPs provide a mathematical formalism how
optimal substructure in the environment can be recursively exploited
when confronted with complicated decisions.
Algorithmic gains by injecting stochasticity in the recall of past
actions and outcomes to improve the internal world model may explain why
very accurate memories have been disfavored in human evolution
and why human creativity might be adaptive.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of intelligent RL systems.
The proposed machine-learning perspective
on DMN function is hence not only practically computable but
also neuroscientifically falsifiable.
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on the default mode network.
%
Ultimately,
the DMN can be viewed as a smoothing kernel extending
from the relatively recent events to anticipated upcoming events
to constantly improve sensory processing and
action performance in the world.

@@

\appendix
\section{Free-energy principles!}
The so-called free-energy principle in its present form (including notions like ``generative density'', ``recognition density'', etc.) can be traced back to works of Dayan \& Hinton \citep{dayan1995helmholtz} in which they introduced the so-called \textit{Helmholtz machine}, a hierarchical factorial directional deep belief-net (DBN).
In this subsection, we will develop from first-principles, the bare-bones minimalistic ideas needed to build a free-energy principle for general decision-making. This ideas were first developed by Hinton et al. in the early 90s in building their Helmholtz machine. Theories like Friston's free-energy principle and active-inference will then emerge as particular instances of this general framework, with particular design choises. For example the Friston theory axiomatizes that the brain uses a (problematic, as it implicitly assumes that posterior of each hidden unit is factorial) wake-sleep algorithm to train the underlying Helmholtz machine, etc.

>>>>

RL is a problem-solving technique in which, through their interactions with an external environment,
an agent learns to reach goals, optimize reward signals, or minimize costs
in an iterative trial-by-error fashion.
At any moment, each taken \textit{action} $a$ triggers a changes in the
\textit{state} of the environment
$s \rightarrow s'$, accompanied by environmental feed signals as \textit{reward}
$r = r(s, a)$ (or regret!, since it can be negative) collected by the
agent.
In this view, the environment is partially controlled by
the action of the agent and the reward should be thought
of as satisfaction -- or punishment -- accompanying the execution of
an action.
Action may be delayed to achieve substantial increases in expected reward
that can increase over time.
The environment is generally taken as stochastic,
that is, unpredictable, changing in random ways. In addition,
it is only \textit{partially observed},
in the sense that only part of the current state is observed by
the agent \citep{starkweather2017dopamine}.
This unpredictability of the environment
is realistic in a model which sets out
to explain DMN function. Indeed, it is known that the more the external world is predictable,
the more mental activity becomes detached from the actual sensory inputs
\citep{antrobus1966studies, pope1978regulation},
the more stimulus-independent thoughts occur, and
the higher the neural activity in the DMN.
Conversely, the more the currently executed task is unknown and unpracticed,
the lower the DMN activity
\citep{filler1973daydreaming, teasdale1995stimulus}.
%
These ``offline'' processes may however contribute to
optimizing control of the organism.
Such a framework of DMN funtion based on reinforcement learning
can naturally embed human behavior
in the tension between exploitative action with immediate gains and
explorative action with longer-term reward schedules
\citep{dayan2008decision}.
The implication of the DMN in a diversity of
particularly advanced cognitive processes
can be parsimoneously explained as prediction error minimization
coupled with probabilistic simulations in form of mental scenes,
thus calibrating action portfolios and
maximizing reward outcome at various time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo (MCMC) sampling
\citep{tenenbaum2011grow}.

@@

Computing an optimal policy then corresponds to finding the parameters $\theta^Q_{k+1}$ which minimize the following mean-squared loss function
\begin{equation}
  \mathcal L(\theta^Q_{k+1})
  % = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}[(Q(s, a|\theta^Q) - Q(s',a'|\theta^Q_{k+1}))^2]
  = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}\left[\frac{1}{2}(Q(s, a|\theta^Q_{k+1}) - y)^2\right],
  \label{eq:oracle}
\end{equation}
where
$ y = r + \gamma \max_{a' \in \mathcal A} Q(s', a'|\theta^Q_k) = r + \gamma Q(s', \pi(s')|\theta^Q_k)$ is the prediction target.
% While $y_t$ is also dependent on $\theta^Q$, this is typically ignored.
For instance, a general linear model with a kernel $\phi$ would be of the
form
$${Q}(s, a|\theta^Q) = \phi(s,a)^T\theta^Q.$$
$\phi(s,a)$ would represent a high-level hand-crafted representation in an
appropriate form of the state-action pairs $(s,a)$,
as proposed by \cite{songNIPS2016}.
%  and Parr et al. 2003 (JMLR)].
A recently proposed breakthrough alternative
\citep{mnih2015,silver2016mastering}, is to learn this
representation using a deep neural net, leading to the so-called \textit{Deep Q-learning} family of methods which
are by far the current state-of-the-art in RL. In such a case, $\theta^Q$
would correspond to the strengths of low-level synaptic or high-level functional connections between different elements
in brain networks.
\textbf{XXX perhaps add one sentence to rephrase and detail the idea}

Learning (i.e., fitting)
of the the entire model parameters can effictively be achieved via \textit{backprop},
wherein prediction errors (i.e., \textit{regrets})  are propagated from lower to higher regions to modulate the choice of future actions
% online stochastic gradient descent is used to minimize the variational objective
% \eqref{eq:oracle}.

@@

\begin{mdframed}
\textbf{A note on classical RL algorithms.}
Note that most RL algorithms, including \textit{Temporal Difference (TD)}
learning \citep{sutton1998reinforcement}, REINFORCE \citep{williams1992}, and SARSA can be
cast in this general variational framework. For instance, TD corresponds to
the above framework using a linear value approximator with feature encoding
$\phi(s,a) = \delta_{(s,a)} =  \text{ point mass at }(s,a)$ on the grid
$\mathcal S \times \mathcal A$, and so
$$\nabla_{\theta^Q_{k+1}}Q(s, a|\theta^Q_{k+1}) = \phi(s, a) = \delta_{(s,a)}.$$
%% Whence, the gradient update due to the sample $(s,a,r,s') \in \mathcal D$ is
%% $$\theta^Q(s,a) \leftarrow \theta^Q(s,a) + (Q(s, a|\theta^Q_{k+1}) - y)$$ ??
\end{mdframed}

\subsubsection{Excursion: The role of the hippocampus}
\paragraph{Does the hippocampus do Monte-Carlo sampling?}
In RL, Monte-Carlo simulation can be used to update the agent's belief state
\citep{silver2010monte}. Such methods have a sample complexity that is determined only by the underlying difficulty of the POMDP, rather than the size of the state space or observation space,
which can be prohibitively large.
Monte-Carlo simulation provides a simple method for evaluating the value / fitness of a state.
They provide an effective mechanism both for tree search and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than a RL agent without stochastic resampling procedures.

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
observations and rewards. These simulations would be used to update the value function, without ever looking inside the black box describing the model's dynamics. This would be a simple control algorithm by evaluating all legal actions and selecting the action with
\textbf{highest expected cumulative rewards [please double-check]}.
In these challenging POMDPs, Monte-Carlo simulation provides an effective mechanism both for tree search and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.
Much recent work points to Monte Carlo or stochastic sampling– based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. For sampling-based methods it is still almost non-existent beyond the description of receptive fields.

\paragraph{Hippocampal replay corresponds to inverse reinforcement-learning?}
%\begin{mdframed}
  Given the trace $s_0,a_0,s_1,\ldots,$ of an optimal agent's strategy $\pi^*$ in
  a POMDP (called a \textit{teacher's demonstration}), can we figure out what is the
  (instantaneous) reward function $r: \mathcal S \times \mathcal \mathcal A
  \rightarrow \mathbb R$ that the agent is optimizing over a prescribed class of reward functions
  (e.g., linear rewards $r(s,a) \equiv \theta^T\phi(s,a)$)?
  For instance, given traces of motor actions from a an adult to grab a cup on a table,
  can an observing child figure out what ``langragian'' functional is being minimized by the former?
  How? Can they reproduce this optimal behavior?
%\end{mdframed}
Such questions are of course pertinent to our decision-making theory for the DMN.
In the general artificial case, the problem has been extensively studied and partially solved by
\cite{abbeel2004}. They are also been rigourously studied in general optimal control literature under the name
``inverse optimal control'', but in model-based certain (where the physical dynamics are known, etc.)...

@@

\subsection{Putting everything together}
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{rl_process_chart.pdf}
  \caption{The DMN as an RL agent... \textbf{Please add a figure caption}}
  \label{fig:rl_process_chart}
\end{figure}
The DMN is today known to consistently increase in neural
  activity when humans engage in goal-directed behavior that are detached from
  current sensory environment \citep{kenet2003spontaneously, fiser2004small}
  and it was proposed to be situated at the top of the functional network hierarchies
  \citep{carhart2010default, margulies2016situating}.
  Its involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the implicit computation of
  action and state cascades as a function of what happened in the past.
% A policy represents the repertoire of possible actions
%   on the world given a current state. It encodes the probabilites of
%   choosing actions to be executed in a certain situation.
% Interactions between external and internal sources of
%   information are probably commonplace during perception \citep{gershman2010learning}
The DMN may subserve
  constant exploration of possible future actions and their
  cumulative outcomes. Implicit computation of future choices
  provides an explanation for the
  evolutionary emergence and practical usefulness of mind-wandering
  in humans.

The HC may provide perturbed action-transition-state-reward samples
  as a block of "imagined", "hypothesized", "recalled" experience.
  The small variations in these experience blocks allow searching
  a larger space of model parameters and possible experiences.
  Taken to its extreme, stochastic recombination of experience
  building blocks can further optimize the behavior of the RL agent
  by model learning from scenarios in the environment that the agent might
  only very rarely or never encounter.
  In the absence of environmental input and feedback
  (e.g., mind-wandering or sleep) pseudo-experiencing (i.e., emulating) possible
  future scenarios and action outcomes.
  Our approach acknowledges the unavoidable stochasticity of
  computation in neuronal processes \citep{faisal2008noise}.

  In our proposed model-free RL-based view, \textit{inference} in the human brain reduces to
  generalization of
  policy and value adaptations from sampled experiences to
  successful action choices and reward predictions in future states.
  As such,
  plasticity in the DMN arises naturally:
  If an agent behaving optimally in a given environment moves
  to novel, yet unexperienced environments, reward prediction errors will
  massively increase. This will lead to adaptation of the policy until the system converges to a 
  new steady-state of optimal action decisions in volatile environments.

@@

% \begin{figure}[!tb]
%   \centering
%   \includegraphics[width=.8\linewidth]{vae.pdf}
%   \caption{Variational autoencoders...}
%   \label{fig:vae}
% \end{figure}
The main algorithm for minimizing free-energy $F_G^R(\x)$ is the \textit{wake-sleep algorithm}.
\citep{dayan1995helmholtz}. As noted already in \citep{dayan1995helmholtz},
a crucial drawback of the wake-sleep algorithm is that it requires a concurrent models (generative and recogntiion), which together do not correspond to optimization of (a bound of) the marginal likelihood (because of the incorrect KL used therein, etc.). Thus the brain could not possible be running such a algorithm, not even in principle! To the rescue, we note that the recent theory of
\textit{variational auto-encoders (VAEs)} \citep{kingma2013auto} might provide an efficient alternative to the wake-sleep algorithm, as it overcomes the technical limits of the former, by using a reparametrization trick. For instance, unlike the wake-sleep algorithm for minimizing free-energy, VAEs can be efficiently trained via back-propagation of learning errors.

@@

\textbf{XXX Your focus in this subsection ought to be on the SC itself not POMPDs, etc.}
 \begin{itemize}
    \item Processing social information has been proposed to underlie the
    physiological baseline of human brain function
    \citep{schilbach2008minds}. This was later challenged by observing
    analogues of the DMN in monkeys \citep{mantini2011default}
    and rats \citep{lu2012rat}, with
    supposedly less advanced social capacities.
    The MDPs parsimoneously explain the dominance of social content in
    human mental scenes by their extremely high relevance to humans
    reflected by high values for social information in the value matrix
    \citep{baker2009action}.
    \item How can a same neurobiological circuit be equally important
    for baseline house-keeping functions and specific task performance?
    Our computational account can explain why the DMN is implicated
    in both a goal-directed task and an idlying rest cognitive set,
    if environmental relevance is processed, manipulated, and retained
    also as a baseline function of human mental activity.
    In tasks, the policy and value matrices are updated to optimize short-term action,
    whereas, at rest, these parameter updates may
    improve especially mid- and long-term action.
    \item The sentinel account does not provide a formal mechanisms of
    how attention and memory resources are exactly reallocated when
    encountering a salient environmental stimulus. \textbf{XXX remove the next sentence. Danilo: can you help me to correct the sentence instead.
    There appears to be a cool link between cognition and formal theory
    here.}
    In contrast,
    the Bellman recursion is weighted at each step by
    $\sum_{a \in A}\pi(a|s)$. This factor weighs which action cascades
    are recursively explored by the agent and which decision trees are neglected.
    This directly implies allocation of attention and computational load.
    \item In sum,
    MDPs imply a ``radar'' function of monitoring the environment for salient information
    in general and explain social thinking as a physiological brain baseline
    as an important special case, without excluding other topics
    contemplated in continuous mental activity.
 \end{itemize}

\section{Conclusion}
What brain function could be important enough
for the existence and survival of the human species
to warrant constant, high energy costs?
MDPs provide an attractive
process model how the human association cortex
might implement supra-modal representation and control of the environment to
optimize the organism's fate.
% by obtaining reward and avoiding pain.
This idealized process model explains
a number of previous experimental observations in the
DMN by a simple but non-trivial mechanism.
%
From the computational view of a Markovian sequential decision process,
behavior unfolds by integrating happened past events
and possible future events to guide action choice in the present context.
This functional account is more compatible with the DMN's
poorly understood involvement across
autobiographical memory retrieval, problem solving,
abstract reasoning based on internally generated scenes, social cognition,
as well as delay discounting and self-related prospection.
MDPs provide a mathematical formalism how
optimal substructure in the environment can be recursively exploited
when confronted with complicated decisions.
Improvement of the internal world model
by injecting stochasticity in the recall of past
actions and outcomes may explain why
very accurate memories have been disfavored in human evolution
and why human creativity might be adaptive.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of intelligent RL systems.
The proposed machine-learning perspective
on DMN function is hence not only practically computable but
also neuroscientifically falsifiable.
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on the default mode network.
%
Ultimately,
the DMN can be viewed as a functional integrator
from the relatively recent events to anticipated upcoming events
in order to constantly improve present action in the world.

@@

\appendix
\section{Free-energy principles!}
The so-called free-energy principle in its present form (including notions like ``generative density'', ``recognition density'', etc.) can be traced back to works of Dayan \& Hinton \citep{dayan1995helmholtz} in which they introduced the so-called \textit{Helmholtz machine}, a hierarchical factorial directional deep belief-net (DBN).
In this subsection, we will develop from first-principles, the bare-bones minimalistic ideas needed to build a free-energy principle for general decision-making. This ideas were first developed by Hinton et al. in the early 90s in building their Helmholtz machine. Theories like Friston's free-energy principle and active-inference will then emerge as particular instances of this general framework, with particular design choises. For instance, the Friston theory axiomatizes that the brain uses a (problematic, as it implicitly assumes that posterior of each hidden unit is factorial) wake-sleep algorithm to train the underlying Helmholtz machine, etc.
